Binning Strategies and Related Loss for Large Data

### 2015-12-18 versionForJCGS/PaperJCGS.Rnw

<<FlightMinBinScat, echo=F,include=F, cache=TRUE>>=
source("RectangularBinningFunctions.R")
load(file="./data/DepartDelaysMinutes.RData")
# Create minimal binning
departure1minute <- RectBin2d(xs=DepartDelaysMinutes$Scheduled,ys=DepartDelaysMinutes$Actual, 
                              originx = -0.5, originy = -0.5, 
                              widthx = 1, widthy = 1, type="standard")
# down to 3.261% of original number of rows
# nrow(departure1minute)/nrow(DepartDelaysMinutes)
ggplot(aes(x=binxs/60, y=binys/60), data=departure1minute) +
  geom_tile( aes(fill=binfreq) ) + 
  scale_x_continuous("Scheduled Departure Time", limits=c(0,24), breaks=seq(0,24,by=6)) +
  scale_y_continuous("Actual Departure Time", limits=c(0,24), breaks=seq(0,24,by=6)) +
  ggtitle("Minimally Binned Scatterplot of Airline Departure Times")+ 
  scale_fill_gradient("Frequency", low="#56B1F7", high="#132B43", guide="legend", trans="log", breaks=c(1, 10, 100, 1000)) +
  theme_bw() + theme(aspect.ratio=1,
                   panel.grid= element_blank(),
                   legend.text=element_text(size=12) ) + 
  geom_abline(intercept=0,slope=1, color="gray70", linetype=3)
ggsave(filename = "./figure/MinimalBinnedAirline2014.png", width= 6.5, height=6, dpi=300)
@

>>>>

<<FlightMinBinScat, echo=F,include=F, cache=TRUE>>=
source("./data/RectangularBinningFunctions.R")
load(file="./data/DepartDelaysMinutes.RData")
# Create minimal binning
departure1minute <- RectBin2d(xs=DepartDelaysMinutes$Scheduled,ys=DepartDelaysMinutes$Actual, 
                              originx = -0.5, originy = -0.5, 
                              widthx = 1, widthy = 1, type="standard")
# down to 3.261% of original number of rows
# nrow(departure1minute)/nrow(DepartDelaysMinutes)
ggplot(aes(x=binxs/60, y=binys/60), data=departure1minute) +
  geom_tile( aes(fill=binfreq) ) + 
  scale_x_continuous("Scheduled Departure Time", limits=c(0,24), breaks=seq(0,24,by=6)) +
  scale_y_continuous("Actual Departure Time", limits=c(0,24), breaks=seq(0,24,by=6)) +
  ggtitle("Minimally Binned Scatterplot of Airline Departure Times")+ 
  scale_fill_gradient("Frequency", low="#56B1F7", high="#132B43", guide="legend", trans="log", breaks=c(1, 10, 100, 1000)) +
  theme_bw() + theme(aspect.ratio=1,
                   panel.grid= element_blank(),
                   legend.text=element_text(size=12) ) + 
  geom_abline(intercept=0,slope=1, color="gray70", linetype=3)
ggsave(filename = "./figure/MinimalBinnedAirline2014.png", width= 6.5, height=6, dpi=300)
@
